\newcommand{\qone}{
Write a shell script to print the prime numbers in a given range. The range is to be supplied as command line arguments.
}

\newcommand{\qtwo}{
Write a shell script to print the following pattern:
\begin{center}
\ttfamily
~~~~~1 \\
~~~~~1 1 \\
~~~~~1 2 1 \\
~~~~~1 3 3 1 \\
~~~~~1 4 6 4 1 \\
\end{center}

}

\newcommand{\qthree}{
Write a shell script which deletes all lines containing the word college from the file supplied as command line argument.
}

\newcommand{\qfour}{
Write a shell script which prints the contents of a text file from line number m to line number n, m and n are supplied from command line argument.
}

\newcommand{\qfive}{
Write a shell script to display all the lines of a file, starting with a vowel. Provide the file name as the command line argument.
}

\newcommand{\qsix}{
Write a shell script that receives any number of filename as any nu me as arguments and check if every argument supplied as a file or a directory and report accordingly. Whenever the arguments are in a file, the number of lines of it is also reported.
}

\newcommand{\qseven}{
Write a shell script that takes a name of a folder as a command line argument, and produce a file that contains the names of all sub folders with size 0 (that is empty sub folders).
}

\newcommand{\qeight}{
Write a shell script to simulate 'wc' command.
}

\newcommand{\qnine}{
Write a shell script to perform bubble sort on an array of numbers. If 1 is given in command line argument, array will be sorted in ascending order and if 2 is given, array will be sorted in descending order.
}

\newcommand{\qTen}{
Write a shell script/shell program to print Fibonacci series. The range input is to be supplied as command line argument.
}

\newcommand{\qEleven}{
Write a shell script to find the second highest number from a list of numbers without using sorting.
}

\newcommand{\qTwelve}{
Write a shell script to perform binary search on a set of data.
}

\newcommand{\qThirteen}{
Write a shell script to prepare word frequency of a given text file.
}

\newcommand{\qFourteen}{
Write a shell script that will take an input file and remove identical lines (or duplicate lines from the file).
}

\newcommand{\qFifteen}{
Write a program that transfers data from one file to a new file excluding vowels.
}

\newcommand{\qSixteen}{
Write a shell script to find the roots of a quadratic equation \( ax^2 + bx + c = 0 \), where \( a \ne 0 \). Consider all the cases.
}

\newcommand{\qSeventeen}{
Write a shell script to perform selection sort on an array of numbers in descending order.
}

\newcommand{\qEighteen}{
Write a shell script to perform the GCD of two integers.
}

\newcommand{\qNineteen}{
Write a shell script to implement a calculator performing addition, subtraction, multiplication and division operations using menu driven concept. The choice of operation must be taken through command line argument.
}

\newcommand{\qTwenty}{
Write a shell program to check whether the given number and its reverse are same. Take the input through command line argument.
}

\newcommand{\qTwentyone}{
Write a shell script to convert the file content from lower case to upper case or upper case to lower case using menu driven concept.
}

\newcommand{\qTwentytwo}{
Write a shell script to implement bubble sort method.
}

\newcommand{\qTwentythree}{
Write a shell script to draw the following pattern.
\begin{center}
    \ttfamily
~~~~*\\
~~~~**\\
~~~~***\\
~~~~****\\
~~~~***\\
~~~~**\\
~~~~*\\
\end{center}

}

\newcommand{\qTwentyfour}{
Write a shell script to print prime factors of a given number, supplied as command line argument.
}

\newcommand{\qTwentyfive}{
Write a shell script that takes a word from the user and find out the frequency of the word in a given file.
}

\newcommand{\qTwentysix}{
Write a shell script to check whether a given word is a palindrome or not. The size of the word must be at least of 4 characters.
}

\newcommand{\qTwentyseven}{
Write a shell script to count the words, lines and characters of a given file. File name should be provided at run time.
}

\newcommand{\qTwentynine}{
Write a shell script that gets executed at the moment of user login and it displays Good Morning,Good afternoon, Good Evening, Good Night, depending upon the time at which the user logs on.
}

\newcommand{\qThirty}{
Write a shell script to find a number using sequential search method.
}

\newcommand{\qThirtyone}{
Write a shell script to find a number using binary search technique.
}

\newcommand{\qThirtytwo}{
Write a shell script to find out the factorial of a given number.
}

\newcommand{\qThirtythree}{
Write a shell script to reverse a string and check whether it is a palindrome.
}

\newcommand{\qThirtyfour}{
Write a shell script for menu-based system to insert records for employees with employee ID, name, designation, salary in a data file, also display records when necessary. Display salary for the employee asked.
}
